Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2021-12-15 ms/SI.tex
first commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\date{}

@@

%
% variables for title and author
%
\usepackage{titling}
\title{}
\author{}

@@

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{}
  \chead[]{}
  \rhead[]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

@@

Sources and consequences of mismatch between leaf disc and whole-leaf
leaf mass per area (LMA)

\[ \]

Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
Chen\textsuperscript{1,3}

\[ \]

\textsuperscript{1} CAS Key Laboratory of Tropical Forest Ecology,
Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences,
Menglun, Yunnan 666303, China

\textsuperscript{2} University of Chinese Academy of Sciences, Beijing
100049, China

\textsuperscript{3} Center of Plant Ecology, Core Botanical Gardens,
Chinese Academy of Sciences, Yunnan 666303, China

\textsuperscript{4} Graduate School of Agriculture, Kyoto University,
Kyoto 606-8502, Japan

\[ \]

\textbf{Corresponding Authors}:

Masatoshi Katabuchi

E-mail:
\href{mailto:mattocci27@gmail.com}{\nolinkurl{mattocci27@gmail.com}}

Jiao-Lin Zhang

Tel: +86 691 871 3046; Fax: +86 691 871 5070; E-mail:
\href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}

\[ \]

Manuscript received \_\_\_\_\_\_\_; revision accepted \_\_\_\_\_\_\_.

\textbf{Running title}: Leaf disc and whole-leaf LMA

@@

\hypertarget{abstract}{%
\section{ABSTRACT}\label{abstract}}

\textbf{PREMISE:} Leaf mass per area (LMA), which is the key trait in
leaf economic spectrum and plant growth analysis, is measured from leaf
discs or whole leaves. These differences in the measurement methods may
lead to large differences in the estimates of LMA values.

\textbf{METHODS:} We determined LMA using leaf discs and whole-leaf
(including petiole) for 334 woody species from across biomes (tropics,
subtropics, savanna, and temperate) to examine what extent whole-leaf
and leaf disc LMA match, whether the differences in the estimates are
associated with leaf size and thickness, and whether intraspecifc
variation for each species match.

\textbf{RESULTS:} Disc-based estimates of species and individual mean
LMA matched well whole-leaf estimates. Thin and large leaves had weaker
correlations between leaf disc and whole-leaf estimates. Variability of
LMA estimates within species (i.e., amount of intraspecific variation)
only weakly matched between whole-leaf and disc-based estimates
(\emph{R\textsuperscript{2}} = 0.31). We also found that sample with
small total dry mass of leaf discs tended to show greater differences
between leaf disc and whole-leaf LMA.

\textbf{CONCLUSIONS:} Mean values of leaf disc LMA are generally good
proxies for mean values of whole-leaf LMA with appropriate calibration
(9.4\% differences in our samples), but their accuracy depends on leaf
size, leaf thickness, and sizes of leaf punch. Therefore, using
appropriate sizes of leaf punch is important for obtaining stable
estimates of leaf disc LMA that matches well with whole-leaf LMA.
Quantifying trait variation using leaf disc should be considered with
caution.

\textbf{Key words:}

intraspecific variation, leaf density, leaf economic spectrum, leaf
heterogeneity, leaf punch, leaf size, leaf thickness, petiole, specific
leaf area, within-leaf variation

\hypertarget{introduction}{%
\section{INTRODUCTION}\label{introduction}}

Leaf mass per area (LMA), determined by lamina thickness and leaf tissue
density (LD), describes how much biomass is invested into given
photosynthetic leaf area thus reflecting a cost for light interception,
which is the key trait of the leaf economic spectrum (LES)
(\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
\protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009};
\protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}). Generally,
resource-acquisitive species (fast-growing species) tend to have low LMA
values, showing high photosynthesis, high nutrients, and often have fast
leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al.,
2004}). In contrast, resource-conservative species (slow-growing
species) often have higher LMA values with the opposite patterns
(\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994};
\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
\protect\hyperlink{ref-Reich2014}{Reich, 2014};
\protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}). The LMA is also
frequently used in plant growth analysis
(\protect\hyperlink{ref-Evans1972}{Evans, 1972};
\protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014};
\protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because
relative growth rates (RGR) can be decomposed into the product of net
assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR
\(\times\) LMR \(\times\) LMA\textsuperscript{-1}). Another appealing
feature of LMA is that it is relatively easy to measure large numbers of
species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et
al., 2004}). Therefore, LMA has been of interests to ecologists and
widely used since the first report more than a century ago
(\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).

LMA values are measured from either 1) a whole leaf including or
excluding petioles, and 2) a leaf disc excluding all major veins or
petioles
(\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et
al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
Although some studies do not make clear what protocol was followed,
these differences in the measurement methods may lead to large
discrepancies in the estimates of LMA values because the major vein
allocation (major vein, which includes first to second or third-order
veins, volume per area) has been reported to be one of the main
determinants for the variation in LMA
(\protect\hyperlink{ref-John2017}{John et al., 2017}). Since larger
leaves should invest more of their mass into dense midribs and petiole
for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al.,
2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves
have clearly visible and large-diameter veins with less uniform leaf
structure {[}i.e., kite-type leaves; Grubb
(\protect\hyperlink{ref-Grubb1986}{1986}){]}, discrepancies in the
estimates of whole-leaf LMA and leaf disc LMA might be greater for
larger and thinner leaves. If leaf disc LMA largely underestimates
whole-leaf LMA, some calibrations may be required to combine or compare
those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et
al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If
divergencies between the estimates based on the different methods are
large (i.e., low \emph{R\textsuperscript{2}} values), this is difficult
to calibrate and should inflate errors in the subsequent analyses. To
date, however, only a database from a single region, Panama Plant Traits
Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is
available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al.,
2020}) that have both estimates of LMA from small leaf discs and whole
leaves including petioles, limiting of our understanding of under what
conditions estimates of LMA from leaf discs are reliable estimates of
whole-leaf LMA.

Given that leaf disc samples have more sources of intraspecific trait
variation (ITV) than whole-leaf samples, the effects of discrepancies
between whole-leaf LMA and leaf disc LMA might be large when ITV is
quantified as a coefficient of variance (CV). Sources of ITV for
whole-leaf samples is variation among individuals within the same
species and variation among leaves within the same individuals
(\protect\hyperlink{ref-Messier2010}{Messier et al., 2010},
\protect\hyperlink{ref-Messier2017}{2017}). An additional source of
trait variation for leaf disc samples is variation among leaf discs
within the same leaves. Thus, extents of ITV for each species based on
whole-leaf and leaf discs samples may not match. Despite the importance
of ITV in community ecology
(\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013};
\protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect
of different measurement methods on the extent of ITV has been largely
ignored.

In this study, we aimed to investigate to which extent whole-leaf
(including petiole) and leaf disc LMA match, whether the relationships
between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
thicknesses, and whether amounts of intraspecifc variations for each
match between whole-leaf and leaf disc based estimates. We collected a
total of 334 woody species from across biomes (tropics, subtropics,
savanna, and warm-temperate) to cover the wide range of geography. We
predicted that the overall relationship between whole-leaf LMA and disc
LMA would be weaker than previous reported LMA data
(\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
0.92 for leaf laminas in Onoda et al.
(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data
with various leaf sizes from the wide range of climates. We also
predicted that species with larger and/or thinner leaves would show
weaker correlations. Finally, we predicted that amounts of intraspecifc
variations for each species do not match well between whole-leaf and
leaf disc based estimates.

\hypertarget{materials-and-methods}{%
\section{MATERIALS AND METHODS}\label{materials-and-methods}}

\emph{Data sources}

We used newly compiled individual-level plant datasets from broad
regions to examine the relationship between leaf traits estimates based
on whole-leaf and leaf disc across wide ranges of geography in China and
Japan (Table S1). First, the Yunnan dataset is from forest plots in
Yunnan province, Southwest China, which includes a tropical rain forest
(TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen
wet forest (STF), with a total of 141 species and 846 individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima
island, Japan, with a total of 193 species and 519 individuals. In
total, we used 334 woody species and 1365 individuals. The trait
sampling methodology are slightly different between the Yunnan and the
Yakushima dataset, which we describe bellow.

\emph{Measurements of disc-based and whole-leaf LMA}

At the TRF site, we collected leaf samples from trees within reach of a
canopy crane (88 m tall with a 60 m long boom). In the HDS, and STF
sites, we used 12-m long pruner to collect samples for most of the
target species. In case of tall individuals that out of the reach of
pruner, we used a rope climbing to reach the canopy, then sampled
branches with the long pruner. In Yakushima, we used 15-m poles for our
leaf sampling. At least twelve sun-exposed healthy leaves were sampled
from 3 to 6 individuals for each species. Trait values were averaged at
the species- and individual-level for the analyses. For compound-leaved
species, we referred a leaflet (the minimum photosynthetic unit) as a
single leaf in our study.

To determine what extent LMA values were affected by the different
methods, LMA were determined (i) LMA based on a whole leaf including
petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
small discs were taken from the base, middle and tip of each leaf using
a 0.6-cm diameter hole punch in the Yunnan dataset. Two large discs from
each leaf were taken using a 1.0-cm diameter hole punch in the Yakushima
dataset. Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials
(whole leaves including petioles and midribs) was measured using scanner
and ImageJ software by the R package \emph{LeafArea}
(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
thickness (LT; mm) was measured using a micrometer in three points at
the base, middle and tip of the leaf using a micrometer (Mitutoyo
293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
dataset but not for the Yakushima dataset, which enables us to estimate
whole-leaf and leaf disc leaf tissue density (LD; g
cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
(whole leaves including petioles and midribs, and leaf discs) was
recorded after drying 80°C for over 48 h to constant weight using an
electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
and petiole dry mass were also determined separately (81 out of 193
species) to quantify leaf support costs. Dry mass for leaf discs were
recorded 2-3 discs together for each leaf. Based on those measurements
of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
calculated as the ratio of leaf dry mass to fresh leaf area, and leaf
tissue density (LD; g cm\textsuperscript{-3}) was calculated as the
ratio of LMA to LT. We do not present results of LD in the main text,
because differences between whole-leaf LD and leaf disc LD only depends
on the ratio between whole-leaf LMA and leaf disc LMA and measurement
errors of leaf thickness (Appendix S2).

\emph{Statistical analyses}

Bivariate trait relationships between disc-based and whole-leaf
log-transformed LMA were summarized with variance explained
(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
standardized major axis (SMA) regressions
(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
samples and different leaf area and thickness groups. Species and
individual groups were divided into four categories based on the medians
of leaf area and leaf thickness across all species and all individuals,
respectively: thin and small-leaved, thin and large-leaved, thick and
small-leaved, thick and large-leaved species (individuals). Median
values are as following: small-leaved species (LA \textless{} 29.3
cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
small-leaved individuals (LA \textless{} 34.7 cm\textsuperscript{2}),
and thin-leaved individuals (LT \textless{} 0.26 mm).

The amount of intraspecific variation of LMA was calculated using
coefficient of variation of log-normally distributed data;
\(CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}\), where \(s_{\mathrm{ln}}\) is
the sample standard deviation in the log-transformed data
(\protect\hyperlink{ref-Julious2000}{Julious and Debarnot, 2000}). We
also considered CV on the arithmetic scale; \(CV = s/\bar{x}\), where
\(s\) is the sample standard deviation and \(\bar{x}\) is the sample
mean. However, these two different CV calculations only negligibly
altered the bivariate relationship and did not change our conclusion,
and thus we will report CV of log-normally distributed data in the main
text.

SMA analyses were run using the R package \emph{smatr}
(\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this
included tests for slope heterogeneity and elevation differences between
disc-based and whole-leaf estimates of LMA values. Confidence intervals
of SMA estimates were based on 1000 bootstraps. All statistical analyses
were conducted in R version 4.1.2
(\protect\hyperlink{ref-RCoreTeam2021}{R Core Team, 2021}).

\hypertarget{results}{%
\section{RESULTS}\label{results}}

Disc-based estimates of species mean LMA matched well whole-leaf
estimates (Table 1; \emph{R\textsuperscript{2}} = 0.87 for all species).
Species with thicker and smaller leaves had stronger correlations
between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
There was a negative correlation between species mean leaf area and leaf
thickness (\emph{r} = -0.3, \emph{P} \textless{} 0.05, \emph{n} = 335).
When we pooled all the species, there were significant differences in
intercepts for species mean LMA (Table 1), suggesting that the
whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates
in the arithmetic scale. Large-leaved species also had significant
positive intercepts, suggesting that whole-leaf estimates of LMA were
22.1\% greater than disc-based estimates in the arithmetic scale (Table
1). While intercepts did not differ for small-leaved species (Table 1).

Disc-based estimates of individual mean LMA also showed positive
correlations with whole-leaf estimates but their
\emph{R\textsuperscript{2}} values are smaller than those for the
species means (Fig. 2). Similar to the species-level pattern,
individuals with thicker and smaller leaves had stronger correlations
(Fig. 2). The relationships between whole-leaf LMA : disc leaf LMA and
total dry mass for the leaf disc (we weighted 2-3 discs together), leaf
thickness, and leaf area were heteroscedastic (unequal variance,
\emph{P} \textless{} 0.001). Samples with small total dry mass, thin
leaves, and larger leaves tended to show greater variance (Fig. 2;
Appendix S3). The total dry mass of leaf disc was positively correlated
with both leaf thickness and leaf punch size (Appendix S4). Amounts of
intraspecific variation (CV; coefficient of variation) only weakly
matched between whole-leaf and disc-based estimate (Fig. 3;
\emph{R\textsuperscript{2}} = 0.31).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)},
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
\date{}

@@

%
% variables for title and author
%
\usepackage{titling}
\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
\author{}

@@

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
  \chead[]{}
  \rhead[Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

@@

\hypertarget{appendix-s1}{%
\section{Appendix S1:}\label{appendix-s1}}

Site information. MAT: mean annual temperature, MAP: mean annual
precipitation, SPEI: Standardized Precipitation Evapotranspiration
Index.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.2469}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0926}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0556}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0617}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1173}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1049}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Site name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Vegetation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Elevation (m)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Locations
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MAT (℃)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MAP (mm)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dry period (month)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Canopy height (m)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species number
\end{minipage} \\
\midrule
\endhead
Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35' E & 21 & 1532 &
6 & 35-45 & 60 \\
Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 &
24°32'N,101°01'E & 11.7 & 1931 & - & 25 & 47 \\
Yuanjiang & Hot-dry savanna (HDS) & 480 & 23°28'N, 102°10'E & 24.7 &
732.8 & 6 & 4-6 & 34 \\
Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 19.4
& 4477 & - & - & 193 \\
\bottomrule
\end{longtable}

The site information and climate data referred to Fei et al.
(\protect\hyperlink{ref-Fei2018}{2018}) and Song et al.
(\protect\hyperlink{ref-Song2017}{2017}). The 6-month-SPEI data were
extracted from the Global SPEI database
(\url{http://spei.csic.es/map/maps.html\#months=1\#month=7\#year=2019}).

@@

\hypertarget{appendix-s2}{%
\section{Appendix S2:}\label{appendix-s2}}

Generalization for a relationship between ratios of disc-based and
whole-leaf estimates of leaf mass per area (LMA), leaf tissue density
(LD), and leaf thickness (LT). For the \emph{i} tree individual or
species, the relationship between ratios of disc-based and whole-leaf
estimates of LMA, LD, and LT is:

\[
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
\]

where \emph{d} indicates disc-based estimates, \emph{w} indicates
whole-leaf based estimates.

Because thickness is measured on leaf lamina whether one uses a leaf
disc or a whole-leaf, the expected ratio between thickness for a leaf
disc and a whole-leaf should be 1. The above relationship, therefore,
can be rewritten using lognormally distributed multiplicative error
(\(\epsilon_i\)) on the arithmetic scale:

\[
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
\]

LMA requires two times measurements (mass and area) and LD requires
three time measurements (mass, area and thickness), and thus variance in
the ratio of whole-leaf LD and leaf disc LD should be greater than that
of LMA.

As we expected LD, showed the slightly smaller
\emph{R\textsuperscript{2}} value than LMA (Figure below) in the Yunnan
dataset. We have independent measurement for thickness for leaf discs
and whole-leaves in the Yunnan dataset. If we use the same leaf
thickness values for leaf discs and whole-leaves (i.e.,
LTw\textsubscript{i}/LTd\textsubscript{i} =1), the scatter plots will be
identical for LMA and LD. Consequently, we do not perform further
analyses for LD, because differences between whole-leaf LD and leaf disc
LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
and measurement errors of leaf thickness.

\includegraphics[width=6.25in,height=\textheight]{../figs/fig1.png}

Figure: Relationships between species mean leaf mass per area (LMA) and
leaf tissue density (LD) determined by using whole leaves and leaf discs
for the Yunnan dataset that has both leaf thickness for leaf discs and
whole leaves. Dashed lines indicate 1:1 lines. Blue solid lines indicate
standardized major axis regressions. The 95\% confidence intervals are
presented as the shaded area. All the correlations are significant
(\emph{P} \textless{} 0.001).

\hypertarget{appendix-s3}{%
\section{Appendix S3:}\label{appendix-s3}}

Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry
mass for the leaf disc, (b) leaf thickness, and (c) leaf area. (b) and
(c) follow the same legend. All the relationships were heteroscedastic
(unequal variance, \emph{p} \textless{} 0.001; all the samples were
analyzed together in (a)). Samples with small total dry mass, thin
leaves, and larger leaves tended to show greater variance.

\includegraphics{../figs/LMAratio2.png}

\hypertarget{appendix-s4}{%
\section{Appendix S4:}\label{appendix-s4}}

Summary of multiple regression for log-transformed total dry mass of
leaf discs. The leaf punch size is described as an effect of `1.0 cm
diameter' compared with `0.6 cm diameter'.

\begin{longtable}[]{@{}lllll@{}}
\toprule
& Estimate & SE & t-value & \emph{P} value \\
\midrule
\endhead
(Intercept) & -4.86 & 0.012 & -410 & \textless{} 0.001 \\
log(Leaf thickness) & 0.223 & 0.009 & 23.7 & \textless{} 0.001 \\
log(Leaf area) & -0.092 & 0.01 & -9.27 & \textless{} 0.001 \\
Large leaf punch & 0.391 & 0.021 & 18.7 & \textless{} 0.001 \\
\bottomrule
\end{longtable}

\hypertarget{appendix-s5}{%
\section{Appendix S5:}\label{appendix-s5}}

Relationships between species mean leaf mass per area (LMA) determined
by using whole leaves and leaf discs. Species groups are divided into
four categories on the basis of the medians of the leaf size and leaf
thickness across all the species. Estimates obtained by different leaf
punches are plotted separately in different colors. All the correlations
are significant (\emph{P} \textless{} 0.001).

\includegraphics[width=6.25in,height=\textheight]{../figs/LMA_sp_gr_both.png}

\hypertarget{appendix-s6}{%
\section{Appendix S6:}\label{appendix-s6}}

Relationships between petiole to leaf dry mass ratio and (a) leaf area
and (b) whole-leaf to leaf disc LMA ratio. Blue solid lines indicate
ordinary least squares (OLS) regressions. The 95\% confidence intervals
are presented as the shaded area. All the correlations are significant
(\emph{P} \textless{} 0.001).

\includegraphics[width=6.25in,height=\textheight]{../figs/petiole.png}

\hypertarget{appendix-s7}{%
\section{Appendix S7:}\label{appendix-s7}}

Relationships between coefficient of variation (CV) in LMA determined by
using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and
(b) 1.0 cm diameter leaf punch. Dashed lines indicate 1:1 lines. Blue
solid lines indicate standardized major axis regressions. The 95\%
confidence intervals are presented as the shaded area. All the
correlations are significant (\emph{P} \textless{} 0.01). Note that the
axes are square root scales.

\includegraphics[width=6.25in,height=\textheight]{../figs/fig_cv2.png}

\hypertarget{literature-cited}{%
\section*{LITERATURE CITED}\label{literature-cited}}
\addcontentsline{toc}{section}{LITERATURE CITED}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
Fei, X., Q. Song, Y. Zhang, Y. Liu, L. Sha, G. Yu, L. Zhang, et al.
2018. \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon
exchanges and their responses to temperature and precipitation in forest
ecosystems in {Yunnan}, {Southwest China}}. \emph{Science of The Total
Environment} 616--617: 824--840.

\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
Song, Q.-H., Y.-P. Zhang, L.-Q. Sha, X.-B. Deng, Y. Deng, C.-S. Wu,
Z.-Y. Lu, et al. 2017.
\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature
variability in a tropical rainforest, subtropical evergreen forest, and
savanna forest in {Southwest China}}. \emph{iForest - Biogeosciences and
Forestry} 10: 611.
